---
title: "1. Geometric Eval"
author: "James Monks"
date: "16/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
fs::dir_map(here::here("R"), source)
source(here::here("Self Localisation", "Geometric Localisation", "geometric_self_localisation.R"))
```

# Read Data
The geometric approach to predicting the locations of players does not rely on any training data as it is simply an application of a function. To remain consistent with the rest of the analyses, only the testing data set will be used to evaluate this measure. 

```{r}
# test_data <- read_all_games(10, from_game = 9) %>% 
  # na.omit()
test_data <- read_rds(here::here("data", "test_data.rds"))
```

# Data Processing
We probably don't want to scale the predictor variables here as this would not change the resultant calculations and would add another step to the process. 

This data processing is mostly about selecting only the closest 2 flags and removing unneeded variables (this is not required though as the pmap function only takes the important sections).


# Predictions
Now making predictions of the data using the get position function (see other markdown files)


```{r}
predictions <- test_data %>%
  pmap_df(function(flag_1_angle, flag_1_dist, flag_2_angle, flag_2_dist, flag_1_x, flag_1_y, flag_2_x, flag_2_y, ...) {
    flag_1_angle <- measurements::conv_unit(flag_1_angle, "degree", "radian")
    flag_2_angle <- measurements::conv_unit(flag_2_angle, "degree", "radian")
    get_position(flag_1_angle, flag_1_dist, flag_2_angle, flag_2_dist, c(flag_1_x, flag_1_y), c(flag_2_x, flag_2_y)) %>% as.data.frame()
  }) %>% 
  set_names("x_hat", "y_hat") %>% 
  mutate(number_time = test_data$number_time)
```

# Evaluating
The data will be evaluated by taking the mse of the predictions and the ground truth.

```{r}
x_mse <- mean((test_data$x - predictions$x_hat)^2)
y_mse <- mean((test_data$y - predictions$y_hat)^2)
total_mse <- mean(c(x_mse, y_mse))
glue::glue("MSE Results: x = {round(x_mse)}, y = {round(y_mse)}, total = {round(total_mse)}")
```

# Saving Prediction Data
```{r}
predictions %>% 
  write_rds(here::here("Results Data", "1_geometry.rds"))
```

